Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-27 lloveras_2020.tex
Version Albert 27-Jan-2020 14:05

%% Template.tex; Solar Physics
%% 
\documentclass[namedreferences]{solarphysics}
%
% spr-sola-addons available options:
%  hyperref      -- loads hyperref.sty with options (pdfborder={0 0 0 },urlcolor=blue,breaklinks)
%  nonatbib      -- do not load natbib.sty (style loads it by default)
%  solaromanenum -- makes enumerated list with roman numerals and a single right-bracket
%  linksfromyear -- puts a link on a year citation (hyperref must be loaded). Loaded by default
%  nolinksfromyear -- suppress  linksfromyear
%  optionalrh    -- for optional running title/author
%  showbiblabels -- to show bibitem label at end of bibitem (via \endbibitem command)
%
\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                     % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                    % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}
\usepackage[utf8]{inputenc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Runningheads
%
\runningauthor{D.G.~Lloveras~\etal}
\runningtitle{Comparative Coronal Study of CR-2082 and CR-2208}

@@

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in \albert{particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique \albert{able to provide} a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images \albert{of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona \albert{through DEMT} reconstructions \albert{and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. \albert{Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the \albert{end of the} declining} phase of SC 24. The 3D \albert{DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We \albert{show the} existence of diverse types of temperature structures in the low and mid latitudes of the \albert{streamer belt. We estimate} the heating energy required to keep them \albert{stable, which we argue may} be accounted for by Alfvén waves. \albert{We also show that results of the latest version of the AWSoM model overal} agree with DEMT \albert{reconstructions within a $\approx 20\%$ accuracy. We highlight some details of the AWSoM model that should} be improved to better reproduce \albert{tomographic} results, in particular concerning the source region of the \albert{fast and slow components of the solar wind.}}
\end{abstract}

@@

Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment. To advance our knowledge of the physics of the solar corona, as well as \albert{to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role. Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar \albert{corona at a global} scale.

To study the \albert{3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool. \albert{In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona. This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona. Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM). The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. \albert{A recent review on DEMT was published by \citet{vasquez_2016}. The technique is summarized in Section \ref{demt}.}

\albert{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona. \albert{DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}. More recently,} \citet{lloveras_2017} combined DEMT with PFSS \albert{models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs. Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux \albert{required at the coronal base in order to maintain stable coronal loops}. In this article, \albert{DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space \albert{Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to \albert{1 AU and beyond} \citep{vander_2010, Van2014}. \albert{The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation. As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.

\albert{In this work, the AWSoM model is used with two purposes. Firstly, to provide an MHD model of the coronal magnetic field to be used to study the DEMT results along magnetic field lines. Secondly, to provide thermodynamic results to be compared with those reconstructed by DEMT.}

\albert{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during \albert{the end of the declining} phase of SC 24. \albert{In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} \albert{(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG). In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} \albert{(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

Section \ref{demt} and \ref{awsom} \albert{summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} \albert{details} the method used to trace \albert{the DEMT} results along the field lines of the magnetic model. Section \ref{energia} details \albert{the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative \albert{detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared. \albert{Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.

@@

\albert{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, \albert{artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}

{The solution of the tomographic problem involves {inversion of} a very large sparse matrix. Such inversion problems are characterized by spurious \albert{high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid \albert{when compared to previous reconstructions.}}

\albert{In DEMT, the inner corona in the range of heliocentric heights $\lesssim 1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to $0.01\,\mrsun$ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each voxel, a measure of the temperature distribution of the plasma contained in it. We summarize next the main aspects of DEMT required for the analysis of this work.}

@@

\albert{In this work,} data from three EUV bands \albert{was used:} 171, 193 and \albert{211 \AA\ in} {the} case of AIA, and 171, 195 and \albert{284 \AA\ bands} in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict \albert{the FBEs \citep{nuevo_2015}}. In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the \albert{DEMT technique} we refer the reader to \citet{frazin_2009}.}

@@

\albert{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind. In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.

\albert{Heating of the solar corona is addressed} by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade. This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.

\albert{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions. The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.

\albert{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}. \albert{In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}. This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.

The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$). In reality, the thin \albert{transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients in a global model would require excessive numerical resources. As described in \citet{Lio2009} and \citet{Sok2013}\albert{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.  To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.  At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Since the broadening of the transition region pushes the corona outwards, \albert{the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}

To drive \albert{the AWSoM model, estimates} of the photospheric magnetic field of the Sun \albert{are the main} input. Synoptic magnetograms are used to specify the initial and the boundary conditions of the \albert{magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics. The source surface is taken to be at 2.5 $\mrsun$. The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun. However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies. An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation. These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}. In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208. \albert{Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 \albert{for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208. The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent \albert{equal to} 0.21 and the amplitude equal to \albert{0.18, for both} rotations. The boundary condition for Alfv\'{e}n wave energy is given by the \albert{poynting flux ($S_{A}$)} of the outgoing \albert{wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set \albert{to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}

\albert{The computational domain of the solar corona} extends from 1 to \albert{$24\,\mrsun$}. The spherical grid in the solar corona is radially stretched (with a maximum resolution \albert{of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement (AMR) resolves the angular cell \albert{size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}. \notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.

@@

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = \albert{r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, \albert{for a total of $97,200$ starting points.}

@@

\albert{In the corona, EUV emission is dominated by collisions of the emitting ions with free electrons, so that the radiative power scales as $N_e^2$. The radiative power of an isothermal plasma at temperature $T$ is then computed as $E_r=N_e^2\,\Lambda(T)$, where the radiative loss function $\Lambda(T)$ is calculated by means of an emission model. In this work we used the latest version of the atomic database and plasma emission model CHIANTI \citep{delzanna_2015}. The radiative power in terms of the LDEM is then given by:}

@@

{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a \albert{field line integrated} version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c,
\end{equation}
\noindent
where the \albert{line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

>>>>

\documentclass[namedreferences]{solarphysics}

\usepackage[hyperref,optionalrh,solaromanenum]{spr-sola-addons} % For Solar Physics 
%\usepackage{epsfig}                     % For eps figures, old commands
\usepackage{graphicx}                    % For eps figures, newer & more powerfull
%\usepackage{courier}                    % Change the \texttt command to courier style
\usepackage{amssymb}                     % useful mathematical symbols
\usepackage{color}                       % For color text: \color command
\usepackage{breakurl}                    % For breaking URLs easily trough lines
\def\UrlFont{\sf}                        % define the fonts for the URLs
\usepackage{comment}
\usepackage{setspace}
\usepackage[utf8]{inputenc}

@@

\runningauthor{D.G.~Lloveras~\etal}
\runningtitle{Comparative Coronal Study of CR-2082 and CR-2208}

@@

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images {of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. {Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the {end of the} declining} phase of SC 24. The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt. We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves. {We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy. We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
\end{abstract}

@@

Being the {region} where the solar atmosphere is {heated, the solar wind accelerated}, and where impulsive events such as solar flares and coronal mass ejections are energized, observing and modeling of the solar corona are of great relevance to improving our understanding of the Sun-Earth environment. To advance our knowledge of the physics of the solar corona, as well as {to enhance} and validate three-dimensional (3D) models, information derived from observational data plays a key role. Solar rotational tomography (SRT) is currently the sole observational technique able to provide a quantitative empirical description of the 3D distribution of some fundamental plasma parameters of the solar {corona at a global} scale.

To study the {3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool. {In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona. This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona. Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM). The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. {A recent review on DEMT was published by \citet{vasquez_2016}. The technique is summarized in Section \ref{demt}.}

{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona. {DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}. More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs. Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}. In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}. {The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation. As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.

{In this work, the AWSoM model is used with two purposes. Firstly, to provide an MHD model of the coronal magnetic field to be used to study the DEMT results along magnetic field lines. Secondly, to provide thermodynamic results to be compared with those reconstructed by DEMT.}

{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG). In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

Section \ref{demt} and \ref{awsom} {summarize the DEMT technique and the AWSoM model, respectively.} Section \ref{trace} {details} the method used to trace {the DEMT} results along the field lines of the magnetic model. Section \ref{energia} details {the method that allows determination of the energy input flux at the coronal base.} In Section \ref{demt_res} the quantitative {detailed DEMT analysis of both target rotations is shown,} and in Section \ref{awsom_res} the AWSoM and DEMT results are compared. {Finally, Section} \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.

@@

{As detailed in Section \ref{intro}, target rotations CR-2082 and CR-2208 were selected to carry out DEMT reconstructions, based on data taken by the STEREO/EUVI-B and SDO/AIA instruments, respectively.} The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}

{The solution of the tomographic problem involves {inversion of} a very large sparse matrix. Such inversion problems are characterized by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid {when compared to previous reconstructions.}}

{In DEMT, the inner corona in the range of heliocentric heights $\lesssim 1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to $0.01\,\mrsun$ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each voxel, a measure of the temperature distribution of the plasma contained in it. We summarize next the main aspects of DEMT required for the analysis of this work.}

@@

{In this work,} data from three EUV bands {was used:} 171, 193 and {211 \AA\ in} {the} case of AIA, and 171, 195 and {284 \AA\ bands} in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict {the FBEs \citep{nuevo_2015}}. In each tomographic voxel, the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.} {For a full description of the {DEMT technique} we refer the reader to \citet{frazin_2009}.}

@@

{AWSoM is a three-temperature}, MHD model of the solar corona and inner heliosphere which provides the 3D distribution of density and temperatures as well as the 3D magnetic structure and velocity of the solar wind. In this work, we use AWSoM model simulated results below 1.25 $\mrsun$ to correspond to the DEMT analysis region.

{Heating of the solar corona is addressed} by including the non-linear interaction of forward and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade. This dissipated turbulent energy is distributed over anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature using theories of linear wave damping and stochastic heating.

{The model accounts} for both collisional and collision-less electron heat conduction and does not use ad-hoc heating functions. The extended MHD equations including radiative cooling, heat conduction and wave turbulence within AWSoM \citep{Van2014} are solved using the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme.

{In a previous} version of the model, the cascade time of the major wave was used to determine the wave damping rate \citep{Cha2011, Van2014}. {In its present version, the energy partitioning  improved} by using the Alfv\'{e}n wave number associated with the damping rate as determined by the critical balance condition, which uses the cascade time of the minor wave \citep{Lit2007}. This leads to more electron heating and less solar wind acceleration \citep{Van2019b}.

The inner boundary of AWSoM is located at the base of the transition region (at $\approx$1.0\,$\mrsun$). In reality, the thin {transition region (TR)} has steep gradients in temperature and density as a result of the balance between coronal heating, heat conduction and the radiative losses. To resolve these gradients in a global model would require excessive numerical resources. As described in \citet{Lio2009} and \citet{Sok2013}{, the TR is artificially broaden to be resolved with a} finest grid resolution of 0.001\,$\mrsun$.  To ensure that the base of the TR is not affected by chromospheric evaporation we overestimate the density at the inner boundary, $N_{e}=N_{i}=N_{\odot} =2\times10^{17}$\,m$^{-3}$ corresponding to the isotropic temperature values, $T_{e}=T_{i}=T_{i\parallel}=T_{\odot}=50,000$\,K. The upper chromosphere is required to extend radially for the density to fall rapidly to correct (lower) values \citep{Lio2009}.  At this level, the radiative losses are sufficiently low so that the temperature can increase monotonically with height and form the transition region. Since the broadening of the transition region pushes the corona outwards, {the AWSoM model achieves coronal conditions at height $\approx 1.05\,\mrsun$, below which results can not then be compared to coronal tomographic reconstructions.}

To drive {the AWSoM model, estimates} of the photospheric magnetic field of the Sun {are the main} input. Synoptic magnetograms are used to specify the initial and the boundary conditions of the {magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics. The source surface is taken to be at 2.5 $\mrsun$. The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun. However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies. An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation. These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}. In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208. {Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208. The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations. The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}

{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}. The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement (AMR) resolves the angular cell {size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}. \notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.

@@

{To determine} the electron density and temperature along individual magnetic field lines, first both the thermodynamic results and the magnetic field obtained with the AWSoM model were interpolated into the DEMT grid. Then, the geometry of the field lines is determined by numerical integration of the first order differential equations  ${\rm d}r/B_r = {r\,{\rm d}\theta}/B_\theta = r\,\sin(\theta)\,{\rm d}\phi/B_\phi$, both inwards and outwards, from the specified 3D coordinates of a starting point. In order to evenly sample the whole volume spanned by the DEMT reconstructions, one starting point is selected at the center of each tomographic cell at 6 uniformly spaced heights, ranging from $1.025$ to $1.225\,\mrsun$, and every 2$^\circ$ in both latitude and longitude, {for a total of $97,200$ starting points.}

@@

{In the corona, EUV emission is dominated by collisions of the emitting ions with free electrons, so that the radiative power scales as $N_e^2$. The radiative power of an isothermal plasma at temperature $T$ is then computed as $E_r=N_e^2\,\Lambda(T)$, where the radiative loss function $\Lambda(T)$ is calculated by means of an emission model. In this work we used the latest version of the atomic database and plasma emission model CHIANTI \citep{delzanna_2015}. The radiative power in terms of the LDEM is then given by:}

@@

{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a {field line integrated} version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c,
\end{equation}
\noindent
where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\
